Fluid structure interaction with ETVF

### 2021-07-16 manuscript/paper.tex
Add new structures example UDF and FSI Bendict Rogers scheme

@@

>>>>

One more way of coupling is by using \citet{khayyer2018enhanced} formulation.

\subsection{Total energy of the structure}
\label{sec:total-energy-struct}

\citet{khayyer2018enhanced} had an extra section where he discusses about the
energy conservation properties of the proposed FSI scheme. He discusses
different energies in structure, kinetic energy and strain energy.

@@

\subsection{Static test to test Structure formulation}
\label{sec:static-test}

In \citet{hwang2015development} has a static test where a cantilever beam is
acted upon by a constant load at the tip.
